%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
% With extensive modifications by:
% Aditya Khedekar (aditya0b0@gmail.com)
%https://github.com/aditya0by0
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Aditya}{Khedekar}{ \urlstyle{same}\href{aditya0by0@gmail.com}{aditya0by0@gmail.com }
 | +91-8530083311 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}  
\vspace{5pt}
\subsection{\href{https://www.vit.edu/}{Vishwakarma Institute \\of Technology, Pune}}
\location{B.Tech in Mechanical Engineering}
Grad. May 2021 | Pune, India\\
CGPA : 8.9/10
\sectionsep


\subsection{\href{https://gppune.ac.in/userindex.php}{Government \\Polytechnic, Pune}}
\location{Diploma in Mechanical Engineering}
Grad. May 2018 | Pune, India\\
Percentage : 90.73\%
\sectionsep

\subsection{New Life Centre High School}
\location{Secondary School Education}
Grad. May 2015 | Pune, India\\
Percentage : 90.6\%
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
\vspace{5pt}

Github:// \href{https://github.com/aditya0by0}{\bf aditya0by0} \\

LinkedIn://  \href{https://www.linkedin.com/in/aditya-khedekar-b1979013b/}{\bf Aditya Khedekar} 

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\vspace{5pt}
\subsection{Undergraduate}
\vspace{3pt}
Data Analytics for Engineers \\
Calculus \\
Vector Calculus \\
Linear Algebra \\
Ordinary Differential Equations \& Transform Techniques\\
Partial Differential Equations \& \space Numerical Techniques\\
Numerical Methods for Engineers\\
Probability and Statistics\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\vspace{5pt}
\subsection{Data Science}
\vspace{2pt}
Machine Learning \textbullet{} Deep Learning\\
Jupyter Notebooks \textbullet{} Numpy \\
\textbullet{} Pandas \textbullet{} Matplotlib\\ 

\vspace{8pt}
\subsection{Programming}
\vspace{2pt}
 Python \textbullet{} Matlab \textbullet{}
C \textbullet{} C++ \\
SAP ABAP \\

\vspace{8pt}
\subsection{Database}
\vspace{2pt}
SQL\\
\vspace{8pt}



\subsection{Others}
\vspace{2pt}
Git \textbullet{} GitHub \textbullet{} SAP MDG\\
Solidworks\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Cognizant}
\descript{| SAP MDG Technical Consultant }
\location{Designation : Programmer Analyst Trainee}
\location{July 2021 - Present | Pune, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Performed Sipoc Analysis and Unit Testing for Business Process.
\item Debugged and Identified bugs in existing custom applications. 
\item Enhanced HANA Search Functionality for custom attributes.
\item Gained Knowledge of custom interfaces built in MDG to interact with external System and applications.
\end{tightemize}
\sectionsep

\runsubsection{Cognizant}
\descript{| Internship Trainee }
\location{Jan 2021 – July 2021 | Pune, India}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Trained and tested by the company on SQL, Java, SAP ABAP \& SAP MDG.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{\href{https://github.com/aditya0by0/Projects/tree/main/Regularized\%20Linear\%20Regression\%20-\%20Built\%20From\%20Scratch}{Linear Regression Model - Built from Scratch} }

\location{DataSet - \href{https://www.kaggle.com/nehalbirla/vehicle-dataset-from-cardekho}{\bf CarDekho Vehicle Dataset}}
Built Linear Regression Model from right scratch for CarDekho Vehicle dataset from Kaggle. Also have added regularization functionality to the model. This model works for single and multi-variables problems. 
\sectionsep



\runsubsection{ \href{https://github.com/aditya0by0/Projects/tree/main/Regularized\%20Multinomial\%20Logistic\%20Regression\%20-\%20Built\%20from\%20Scratch}{MultiNomial Logistic Regression - Built from Scratch}}

\location{DataSet - \href{https://archive.ics.uci.edu/ml/datasets/iris}{\bf Iris Dataset}}
Built Logistic Regression model for multi-class Classification with Neural Network design approach and have added regularization parameter to prevent overfitting. 
\sectionsep



\runsubsection{ \href{https://github.com/aditya0by0/Projects/tree/main/PCA\%20-\%20From\%20Scratch}{PCA - Built from Scratch} }

\location{Dataset - Dummy Data}
Along with building model for Principal Component Analysis (PCA) step by step, I have also animated and provided detailed explanation for each step for a beginner to understand.  
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications} 

\runsubsection{ \href{https://www.coursera.org/account/accomplishments/verify/39JPYHMDSVH6}{Machine Learning} }\descript{| Instructor - Andrew Ng }

Issued by Standford University and Coursera
\sectionsep

\runsubsection{ \href{https://www.coursera.org/account/accomplishments/specialization/S6AH7AFB6P7H}{Deep Learning Specialization} }\descript{| Instructor - Andrew Ng }
Issued by deeplearning.ai and Coursera
\sectionsep

\runsubsection{ \href{https://www.coursera.org/account/accomplishments/specialization/25RBVD6KHNFR}{Python for Everybody Specialization} }\descript{}
Issued by Michigan University and Coursera
\sectionsep

\runsubsection{ \href{https://www.coursera.org/account/accomplishments/specialization/7GFWJXRHHR4H}{Python 3 Programming Specialization} }\descript{}
Issued by Michigan University and Coursera
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Language Proficiency
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Language Proficiency} 

\vspace{\topsep} % Hacky fix for awkward extra vertical space

\begin{tightemize}
    \item Japanese - JLPT N4 Certified
    \item German - Basic Proficiency
    \item English - Professional Proficiency
    \item Marathi - Native Proficiency
    \item Hindi - Native Proficiency
\end{tightemize}
    

\end{minipage} 
\end{document}  \documentclass[]{article}
